Relating games of Menger, countable fan tightness, and selective separability

### 2018-03-06 articles/relating-games-menger-cft-ss/article.tex
finish incorporating reviewer's mathematical corrections

Our goal is to now demonstrate a space which is \(CFT^+\),
but not even \(CDFT^{\plusMark}\). To do so, we will find a space \(X\)
which is \(\Omega M^+\) but not \(\Omega M^{\plusMark}\), yielding \(C_p(X)\)
as our example.

@@

  Conversely, assume that for each \(\omega\)-cover
  \(\mc U\) of \(X\) and \(n<\omega\), there exists a finite subcollection
  \(\mc F\in[\mc U]^{<\omega}\) such that for each \(F\in[X]^{\leq n}\)
  there exists some \(U\in\mc F\) where \(F\subseteq U\). Given an
  arbitrary open cover \(\mc V\), close it under finite unions to obtain
  an \(\omega\)-cover \(\mc U\). Then the finite subcollection \(\mc F\)
  of \(\mc U\) is of course a finite subcover,
  and since each member of \(\mc F\) is a finite union of open sets in
  \(\mc V\), there exists a finite subcover \(\mc G\) of \(\mc V\).
\end{proof}

@@

\begin{question}
  Does there exist a non-\(\sigma\)-compact \(\Omega M^+\) space
  with a coarser separable metrizable topology?
\end{question}

@@

\begin{lemma}\label{mainLemma}
  Let \(\mc A\) be a family of sets where
  \(|\bigcup\mc A|\leq\omega\)
  and let \(\mc B\) be a family of sets closed under supersets. Then
  \(\plII\win\schSelGame{\mc A}{\mc B}\) if and only if
  \(\plII\markwin\schSelGame{\mc A}{\mc B}\).
\end{lemma}

@@

  For \(t\in\omega^{<\omega}\), suppose
  \(Z_s\in\mc A\) has been defined for all \(s\leq t\). Note then that
  \(
    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>):A\in\mc A\}
      \subseteq
    [\bigcup\mc A]^{<\omega}
  \)
  and therefore is countable.
  So choose \(Z_{t\concat\<n\>}\in\mc A\) for \(n<\omega\) such that
  \(
    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>):A\in\mc A\}
      =
    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,Z_{t\concat\<n\>}\>):n<\omega\}
  \).

@@

  So let \(\sigma\) witness
  \(\plII\markwin\schSelGame{\Omega_X^*}{\Omega_X^*}\).
  For each \(\omega\)-cover \(\mc U\) and finite set \(F\in[X]^{<\omega}\),
  choose \(U_{\mc U,F}\in\mc U\) such that \(F\subseteq U\). Then choose a
  basic open set \(U_{\mc U,F}^*\) such that
  \(F\subseteq U_{\mc U,F}^*\subseteq U_{\mc U,F}\). Finally, for each
  \(\omega\)-cover \(\mc U\), let
  \[
    \mc U^*
      =
    \{
      U_{\mc U,F}^*
        :
      F\in[X]^{<\omega}
    \}
      \in
    \Omega_X^*
  .\]

  Define the strategy \(\tau\) such that
  \(\tau(\mc U,n)=\{U_{\mc U,F}:U_{\mc U,F}^*\in\sigma(\mc U^*,n)\}\).
  For any sequence of \(\omega\)-covers \(\<\mc U_0,\mc U_1,\dots\>\),
  it follows that \(\bigcup_{n<\omega}\sigma(\mc U_n^*,n)\) is an
  \(\omega\)-cover, and therefore
  \(\bigcup_{n<\omega}\tau(\mc U_n,n)\) is an \(\omega\)-cover also.
\end{proof}

>>>>

Our goal is to now demonstrate a space which is \(CFT^+\),
but not \(CFT^{\plusMark}\) or even \(CDFT^{\plusMark}\).
To do so, we will find a space \(X\)
which is \(\Omega M^+\) but not \(\Omega M^{\plusMark}\), yielding \(C_p(X)\)
as our example.

@@

  Conversely, assume that for each \(\omega\)-cover
  \(\mc U\) of \(X\) and \(n<\omega\), there exists a finite subcollection
  \(\mc F\in[\mc U]^{<\omega}\) such that for each \(F\in[X]^{\leq n}\)
  there exists some \(U\in\mc F\) where \(F\subseteq U\). Given an
  arbitrary open cover \(\mc V\), close it under finite unions to obtain
  an \(\omega\)-cover \(\mc U\). Then for \(n=1\),
  the finite subcollection \(\mc F\) of \(\mc U\) satisfying
  \(\{x\}\subseteq U\) for all \(x\in X\) and some \(U\in\mc U\)
  is of course a finite subcover.
  Since each member of \(\mc F\) is a finite union of open sets in
  \(\mc V\), there exists a finite subcover \(\mc G\) of \(\mc V\).
\end{proof}

@@

\begin{question}
  Does there exist a \(T_{3\frac{1}{2}}\),
  non-\(\sigma\)-compact, and \(\Omega M^+\) space
  with a coarser separable metrizable topology?
\end{question}

@@

\begin{lemma}\label{mainLemma}
  Let \(\mc A\) be a family of sets where
  \(|\bigcup\mc A|\leq\omega\)
  and let \(\mc B\) be a family of sets such that
  \(B\in\mc B\) and \(B\subseteq B'\subseteq\bigcup\mc A\)
  implies \(B'\in\mc B\). Then
  \(\plII\win\schSelGame{\mc A}{\mc B}\) if and only if
  \(\plII\markwin\schSelGame{\mc A}{\mc B}\).
\end{lemma}

@@

  For \(t\in\omega^{<\omega}\), suppose
  \(Z_s\in\mc A\) has been defined for all nonempty \(s\leq t\).
  We use the convention
  \(
    \<Z_{\emptyset\rest1},Z_{\emptyset\rest2},\dots,Z_\emptyset,A\>
      =
    \<A\>
  \).
  Note then that
  \[
    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>):A\in\mc A\}
      \subseteq
    \left[\bigcup\mc A\right]^{<\omega}
  \]
  and therefore is countable.
  So choose \(Z_{t\concat\<n\>}\in\mc A\) for \(n<\omega\) such that
  \[
    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>):A\in\mc A\}
      =
    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,Z_{t\concat\<n\>}\>):n<\omega\}
  .\]

@@

  So let \(\sigma\) witness
  \(\plII\markwin\schSelGame{\Omega_X^*}{\Omega_X^*}\).
  For each \(\omega\)-cover \(\mc U\) and finite set \(F\in[X]^{<\omega}\),
  choose \(U_{\mc U,F}\in\mc U\) and a basic open set \(B_{\mc U,F}\)
  such that \(F\subseteq B_{\mc U,F}\subseteq U_{\mc U,F}\).
  Finally, for each \(\omega\)-cover \(\mc U\), let
  \[
    \mc U^*
      =
    \{
      B_{\mc U,F}
        :
      F\in[X]^{<\omega}
    \}
      \in
    \Omega_X^*
  \]
  be an \(\omega\)-cover of basic open sets refining \(\mc U\).

  Given \(\mc U\) and \(V\in\mc U^*\), choose
  \(F(V)\in[X]^{<\omega}\) such that \(V=B_{\mc U,F(V)}\).
  Define the strategy \(\tau\) such that
  \(\tau(\mc U,n)=\{U_{\mc U,F(V)}:V\in\sigma(\mc U^*,n)\}\).
  For any sequence of \(\omega\)-covers \(\<\mc U_0,\mc U_1,\dots\>\),
  it follows that \(\bigcup_{n<\omega}\sigma(\mc U_n^*,n)\) is an
  \(\omega\)-cover refining \(\bigcup_{n<\omega}\tau(\mc U_n,n)\), and therefore
  \(\bigcup_{n<\omega}\tau(\mc U_n,n)\) is an \(\omega\)-cover also,
  demonstrating that \(X\) is \(\Omega M^{\plusMark}\).
\end{proof}
